---
title: "1 Import Cell Ranger to R"
output: html_document
date: "2024-01-29"
---

```{r}
> #### Pre-Analysis Steps

we are using the Filtered version for the feature/cell matrix because The filtered gene-barcode matrix excludes barcodes that correspond to this background noise (e.g. GEMs with free-floating mRNA from lysed or dead cells) ([Filtered vs Raw Matrix](https://kb.10xgenomics.com/hc/en-us/articles/360001892491-What-is-the-difference-between-the-filtered-and-raw-gene-barcode-matrix-)).

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir ="/Users/leynaxoi/Documents/PLO Mice Run 2/Analysis 2" )
```

> #### Setting Up Seurat Object

###### 1. Setting up working directory

```{r}
setwd("/Users/leynaxoi/Documents/PLO Mice Run 2/Analysis 2")
getwd()
```

###### 2. Creating Folder (*Folder exist? Code will not generate another folder*)

```{r}
#creating an output folder the future data that gets generated 
dir.create("data")
dir.create("results")
dir.create("figures")
```

###### 3a. Loading Libraries

list.of.packages <- c("ggplot2", "Rcpp")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

```{r}
library(Seurat)
library(tidyverse)
library(Matrix)
library(scales)
library(cowplot)
library(RCurl)
library(AnnotationHub)
library(rtracklayer)
library(GPseq)
library(ensembldb)
``` 

###### 4. Load PLO Run 2 (Filtered Cell/Feature matrix)

```{r}
#WT
WT <- Read10X(data.dir = "/Users/leynaxoi/Documents/PLO Mice Run 2/Raw Data /WT/filtered_feature_bc_matrix")
#KO
Het <- Read10X(data.dir = "/Users/leynaxoi/Documents/PLO Mice Run 2/Raw Data /Het/filtered_feature_bc_matrix")
#KO
KO <- Read10X(data.dir = "/Users/leynaxoi/Documents/PLO Mice Run 2/Raw Data /KO/filtered_feature_bc_matrix")
```


```{r}
# Create a merged Seurat object
PLO_Mice <- merge(x = WT, 
                       y = c(Het,KO),
                       add.cell.id = c("WT","Het","KO"))
```


